### 2019-10-01 conflog.tex
fixes positions

\subsection{Conference Facilities}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{garden_dinner.jpg}
    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in round tables.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{ihotel-dinner.png}
    \caption{The current 400-person banquet space at the IHotel is pictured 
        above. A new, 690-person ballroom will be available in 2020.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{illinirooms.jpg}
    \caption{The combined Illini rooms with capacity for 496 in round tables.}
\end{figure}

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. It features complimentary breakfast for its guests every morning. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter buses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\ 
>>>>>>> upstream/master
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

    \end{tabular} 
\end{table}
\noindent\textbf{*}\textit{Estimated assuming an average 23 MPG}\\
\textbf{**}\textit{Assumes four people in a car}

>>>>

\clearpage
\subsection{Conference Facilities}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.4\textwidth]{garden_dinner.jpg}
    \caption{The Garden Hotel Banquet Hall with capacity for 600 people in round tables.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.65\textwidth]{ihotel-dinner.png}
    \caption{The current 400-person banquet space at the I Hotel is pictured 
        above. A new, 690-person ballroom will be available in 2020.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.75\textwidth]{illinirooms.jpg}
    \caption{The combined Illini rooms with capacity for 496 in round tables.}
\end{figure}

@@

$\textbf{The Garden Hotel Urbana}$\\
When selecting the primary hotel to accommodate students we considered the ability to host all students under one roof over proximity to the conference activities. The Garden Hotel Urbana (soon to be the Radisson) will be the primary hotel for all attendees. It features complimentary breakfast for its guests every morning. This will also be the location of the opening ceremony dinner. Since this hotel is just beyond walking distance from the main conference activities (2.2 miles), we will hire four Peoria Charter buses to shuttle attendees to and from the Union every 10 minutes. Additionally, there is a CU-MTD bus stop adjacent to the hotel that travels directly to the Union and runs every 10 minutes from 7am to 5am the following day for weekdays, and every 30 minutes on weekends.\\ 
\begin{figure}[H]
	\centering
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_king.jpg}
		\subcaption{King Suite}
	\end{subfigure}%
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{garden_queen.jpg}
		\subcaption{Queen Double}
	\end{subfigure}
	\caption{Garden Urbana Hotel rooms}		
\end{figure}

@@

    \end{tabular}
\subcaption*{\textbf{*}\textit{Estimated assuming an average 23 MPG} \textbf{**}\textit{Assumes four people in a car}} 
\end{table}

### 2019-10-01 website.tex
fixes positions

\section{Website and Social Media}
\subsection{Website}
Shortly after the host is announced, ANS-UIUC will purchase a domain name and create a website in conjunction with ANS National. The website will be hosted using GitHub pages, a free hosting service for static websites. Since there is no cost, the website can be hosted indefinitely. This webhost was selected because several members of the chapter possess knowledge and experience in using it for serving collaborative, Jekyll-based, and static HTML websites. The domain name can be purchased for as little as one dollar for the first year, and a little less than $\$20$ to maintain annually. If we need to cut costs or decide that a domain name ending in ".github.io" is fine we can drop the purchased domain name. The website will include important dates, costs, calendars, schedules, maps, emergency contact information, as well as a direct link to the paper submission site for the conference. The mobile web app will store downloaded maps, emergency contact information, and calendars for offline use while providing access to all features of the website as well.

>>>>

\section{Website and Social Media}
\subsection{Website}
Shortly after the host is announced, ANS-UIUC will purchase a domain name and create a website in conjunction with ANS National. The website will be hosted using GitHub pages, a free hosting service for static websites. Since there is no cost, the website can be hosted indefinitely. This webhost was selected because several members of the chapter possess knowledge and experience in using it for serving collaborative, Jekyll-based, and static websites. The domain name can be purchased for as little as one dollar for the first year, and a little less than $\$20$ to maintain annually. If we need to cut costs or decide that a domain name ending in ".github.io" is fine we can drop the purchased domain name. The website will include important dates, costs, calendars, schedules, maps, emergency contact information, as well as a direct link to the paper submission site for the conference. The mobile web app will store downloaded maps, emergency contact information, and calendars for offline use while providing access to all features of the website as well.
